Jesse Lu

### 2013-05-21 resume/cv.tex
Added fdtd gpu presentation

\section{PhD Research: Nanophotonic Computational Design and Optimization}
\begin{itemize}
\item Nanophotonic design and optimization was 
    a brute force, trial-and-error process
    which took \emph{weeks to months} to improve a single structure---even with 
    a good initial guess.
\item I had to build a system to design structures within a day,
    solely based on the performance specification of the desired device,
    and without good initial guesses.
\item I applied methods from the field of convex optimization 
    to the physical problem of linear nanophotonic design. 
    I sped up computation by implementing my method on GPUs,
    and achieved scale by leveraging the cloud (Amazon EC2).
\item This resulted in the design 
    of nanophotonic devices that were either
    more compact, more robust, or more efficient 
    than all previous designs.
    Critically, these designs only required a day (or two) of computation,
    and a specification for the intended performance (no good initial guess).
    \end{itemize}

\section{Publications}          
    ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes'' Jesse Lu, Jelena Vuckovic (Optics Express, 2012). \\
    ``Inverse design of a three-dimensional nanophotonic resonator'' Jesse Lu, Stephen Boyd, Jelena Vuckovic (Optics Express, 2011). \\
    ``Inverse design of nanophotonic structures using complementary convex optimization'' Jesse Lu, Jelena Vuckovic (Optics Express, 2010). \\
    ``Numerical optimization of a grating coupler for the efficient excitation of surface plasmons at an Ag-SiO2 interface'' Jesse Lu, Csaba Petre, Josh Conway, Eli Yablonovitch (JOSA B, 2007).

>>>>

\section{PhD Research: Nanophotonic Computational Design and Optimization}
\begin{itemize}
\item Nanophotonic design and optimization was 
    a brute force, trial-and-error process
    which took \emph{weeks to months} to improve a single structure---even with 
    a good initial guess.
\item I built a system to design structures within a day,
    solely based on the performance specification of the desired device,
    and without good initial guesses.
\item I applied methods from the field of convex optimization 
    to the physical problem of linear nanophotonic design. 
    I sped up computation by implementing my method on GPUs,
    and achieved scale by leveraging the cloud (Amazon EC2).
\item This resulted in the design 
    of nanophotonic devices that were either
    more compact, more robust, or more efficient 
    than all previous designs.
    Critically, these designs only required a day (or two) of computation,
    and a specification for the intended performance (no good initial guess).
    \end{itemize}

\section{Publications}          
    ``Nanophotonic Computational Design'' Jesse Lu, Jelena Vuckovic (Optics Express, 2013 \emph{in process}). \\
    ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes'' Jesse Lu, Jelena Vuckovic (Optics Express, 2012). \\
    ``Inverse design of a three-dimensional nanophotonic resonator'' Jesse Lu, Stephen Boyd, Jelena Vuckovic (Optics Express, 2011). \\
    ``Inverse design of nanophotonic structures using complementary convex optimization'' Jesse Lu, Jelena Vuckovic (Optics Express, 2010). \\
    ``Numerical optimization of a grating coupler for the efficient excitation of surface plasmons at an Ag-SiO2 interface'' Jesse Lu, Csaba Petre, Josh Conway, Eli Yablonovitch (JOSA B, 2007).
